decompr: trade flow decomposition for Global Value Chain analysis

### 2014-12-04 README.Rmd
Update README.Rmd

The Wang-Wei-Zhu decomposition goes a step further by not only revealing the source of the value added,
but also breaking down exports into different categories, based on final usage.

* domestic value added - absorbed abroad
* domestic value added - eventually reimported
* foreign value added
* pure double counted terms

>>>>

The Wang-Wei-Zhu decomposition goes a step further by not only revealing the source of the value added,
but also breaking down exports into different categories, based on its usage and final destination.

* domestic value added in exports
* foreign value added in exports
* pure double counted terms
